---
title: "WUP-Linear-Model-with-prediction-nuevo"
author: "David Barton"
date: "2025-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

### Model1: SIMS-ARM

```{r} 
BasicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
BasicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```


### Inferntial Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

### Create target 

```{r}
target <- data.frame(ARM=90, Grip=90)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

### Linear Fit Model 1

```{r}
BasicNN + geom_point() + ggtitle("SIMS~ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20 )) + geom_smooth(method=lm)
```

### Model 2 SIMS~GRIP

```{r} 
BasicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
BasicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

### Inferntial Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

### Linear Fit Model 2

```{r}
BasicNN + geom_point() + ggtitle("SIMS~GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20 )) + geom_smooth(method=lm)
```

### Model 3 SIMS~ARM+GRIP

### Numerical results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation for model 3 is higher compared to model and too model 1. The correlation is better when usuing both models

### Inferntial Results

```{r}
model.3 <- lm(SIMS~GRIP,data=data)
summary.lm(model.3)
```

The formula for getting model3 is fomula = -5.433871 + 0.037311*ARM + 0.24470*GRIP


### Anova Test for models 

### Model1~model3

```{r}
anova(model.1,model.3)
```

Our P Value was 0.000004994 which is small and it tells us model3 is better than model1 in a huge way.


